### 2013-04-10 MSteenhagen-CV.tex
Blocked out ESPP and BPPA stuff
Unblocked ESPP
BPPA stuff now in prof. org.
Several changes

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}

\ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.

@@

\noindent\href{http://www.kent.ac.uk/arts/hpa/index.html}{\emph{University of Kent, History \amper Philosophy of Art} \vspace{0.01in}}

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art, seminar leader and lecturer in aesthetics)

@@

\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Department of  Philosophy}} \vspace{0.01in}

\ind 2011-2012. Teaching Assistant in Philosophy, seminar leader applied ethics

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks (recent)}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

\ind 2011. UCL Representative for the \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association}.

@@

>>>>

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.\\ Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis. \href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}

@@

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art, seminar leader and lecturer in Aesthetics. \href{http://www.kent.ac.uk/arts/hpa/index.html}{\emph{University of Kent, History \amper Philosophy of Art} \vspace{0.01in}}

@@

\ind 2011-2012. Teaching Assistant in Philosophy, seminar leader Applied Ethics. \href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Department of  Philosophy}} \vspace{0.01in}

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks (recent)}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

@@

\ind Representative, \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association} (UCL, 2011).
